### 2022-12-09 dissertation/appendix/symbols.tex
Symbols done

\begin{description}
	\item [\parbox{2cm}{$\alpha_{1}$}]
	\item [\parbox{2cm}{$\alpha_{k}$}]
	\item [\parbox{2cm}{$\alpha_{K}$}]
	\item [\parbox{2cm}{$\alpha$}]
	\item [\parbox{2cm}{$\beta_{1}$}]
	\item [\parbox{2cm}{$\beta_{2}$}]
	\item [\parbox{2cm}{$\beta_{j,k}$}]
	\item [\parbox{2cm}{$\beta_{K}^{J}$}]
	\item [\parbox{2cm}{$\beta$}]
	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}]
	\item [\parbox{2cm}{$\boldsymbol{\beta}$}]
	\item [\parbox{2cm}{$\boldsymbol{\gamma}$}]
	\item [\parbox{2cm}{$\boldsymbol{\hat{\phi}}$}]
	\item [\parbox{2cm}{$\boldsymbol{\hat{\psi}}$}]
	\item [\parbox{2cm}{$\boldsymbol{\hat{\theta}}$}]
	\item [\parbox{2cm}{$\boldsymbol{\lambda}$}]
	\item [\parbox{2cm}{$\boldsymbol{\phi}$}]
	\item [\parbox{2cm}{$\boldsymbol{\psi}$}]
	\item [\parbox{2cm}{$\boldsymbol{\theta}$}]
	\item [\parbox{2cm}{$\boldsymbol{C}$}]
	\item [\parbox{2cm}{$\boldsymbol{E}$}]
	\item [\parbox{2cm}{$\boldsymbol{H}$}]
	\item [\parbox{2cm}{$\epsilon(-1)$}]
	\item [\parbox{2cm}{$\epsilon$}]
	\item [\parbox{2cm}{$\eta$}]
	\item [\parbox{2cm}{$\gamma_{0}$}]
	\item [\parbox{2cm}{$\gamma_{1,k}$}]
	\item [\parbox{2cm}{$\gamma_{1}$}]
	\item [\parbox{2cm}{$\gamma_{2,k}$}]
	\item [\parbox{2cm}{$\gamma_{K}$}]
	\item [\parbox{2cm}{$\hat{\phi}_{j,k}$}]
	\item [\parbox{2cm}{$\hat{\psi_{k}}$}]
	\item [\parbox{2cm}{$\hat{\psi}_{k}$}]
	\item [\parbox{2cm}{$\hat{\theta_{k}}$}]
	\item [\parbox{2cm}{$\hat{\theta}_{k}$}]
	\item [\parbox{2cm}{$\lambda_{1}$}]
	\item [\parbox{2cm}{$\lambda_{j}$}]
	\item [\parbox{2cm}{$\lambda_{J}$}]
	\item [\parbox{2cm}{$\mathbbm{1}_{0}$}]
	\item [\parbox{2cm}{$\mathbbm{1}_{1}$}]
	\item [\parbox{2cm}{$\mathbin{\%}$}]
	\item [\parbox{2cm}{$\mathcal{A}(v)$}]
	\item [\parbox{2cm}{$\mathcal{L}$}]
	\item [\parbox{2cm}{$\phi_{j,k}$}]
	\item [\parbox{2cm}{$\phi_{jk}$}]
	\item [\parbox{2cm}{$\phi$}]
	\item [\parbox{2cm}{$\psi_{k}$}]
	\item [\parbox{2cm}{$\psi_{k}N_{k}$}]
	\item [\parbox{2cm}{$\psi$}]
	\item [\parbox{2cm}{$\theta_{k}$}]
	\item [\parbox{2cm}{$\theta$}]
	\item [\parbox{2cm}{$A$}]
	\item [\parbox{2cm}{$B$}]
	\item [\parbox{2cm}{$Beta$}]
	\item [\parbox{2cm}{$Bin$}]
	\item [\parbox{2cm}{$c_{1}$}]
	\item [\parbox{2cm}{$c_{i,k}$}]
	\item [\parbox{2cm}{$c_{i}$}]
	\item [\parbox{2cm}{$Dir$}]
	\item [\parbox{2cm}{$e_{i,j,k}$}]
	\item [\parbox{2cm}{$e_{i}$}]
	\item [\parbox{2cm}{$e_{j}$}]
	\item [\parbox{2cm}{$E[\phi_{j,k}]$}]
	\item [\parbox{2cm}{$E[\psi_{k}]$}]
	\item [\parbox{2cm}{$E[\theta_{k}]$}]
	\item [\parbox{2cm}{$h_{i,k}$}]
	\item [\parbox{2cm}{$h_{i}$}]
	\item [\parbox{2cm}{$h_{k}$}]
	\item [\parbox{2cm}{$i$}]
	\item [\parbox{2cm}{$I$}]
	\item [\parbox{2cm}{$j$}]
	\item [\parbox{2cm}{$J$}]
	\item [\parbox{2cm}{$K-1$}]
	\item [\parbox{2cm}{$k$}]
	\item [\parbox{2cm}{$K$}]
	\item [\parbox{2cm}{$L$}]
	\item [\parbox{2cm}{$LSE$}]
	\item [\parbox{2cm}{$Mult$}]
	\item [\parbox{2cm}{$N_{0,k}$}]
	\item [\parbox{2cm}{$N_{1,k}$}]
	\item [\parbox{2cm}{$N_{j,k}$}]
	\item [\parbox{2cm}{$N_{j}$}]
	\item [\parbox{2cm}{$N_{k}$}]
	\item [\parbox{2cm}{$N$}]
	\item [\parbox{2cm}{$S$}]
	\item [\parbox{2cm}{$t$}]
\end{description}

@@

\begin{description}
	\item [\parbox{2cm}{$\alpha_{0}$}]
	\item [\parbox{2cm}{$\alpha_{6}$}]
	\item [\parbox{2cm}{$\alpha_{7}$}]
	\item [\parbox{2cm}{$\alpha_{8}$}]
	\item [\parbox{2cm}{$\alpha_{i} = 50$}]
	\item [\parbox{2cm}{$\boldsymbol{{H}}$}]
	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}]
	\item [\parbox{2cm}{$\boldsymbol{\phi}$}]
	\item [\parbox{2cm}{$\boldsymbol{\psi}$}]
	\item [\parbox{2cm}{$\boldsymbol{\theta}$}]
	\item [\parbox{2cm}{$\boldsymbol{C}$}]
	\item [\parbox{2cm}{$\boldsymbol{E}$}]
	\item [\parbox{2cm}{$\boldsymbol{H}$}]
	\item [\parbox{2cm}{$\pm$}]
	\item [\parbox{2cm}{$\theta_{0}$}]
	\item [\parbox{2cm}{$\theta_{6}$}]
	\item [\parbox{2cm}{$\theta_{7}$}]
	\item [\parbox{2cm}{$\theta_{8}$}]
	\item [\parbox{2cm}{$c_{1}$}]
	\item [\parbox{2cm}{$Cat$}]
	\item [\parbox{2cm}{$Dir$}]
	\item [\parbox{2cm}{$e_{0}$}]
	\item [\parbox{2cm}{$h_{0}$}]
	\item [\parbox{2cm}{$h_{6}$}]
	\item [\parbox{2cm}{$h_{7}$}]
	\item [\parbox{2cm}{$h_{8}$}]
	\item [\parbox{2cm}{$i$}]
	\item [\parbox{2cm}{$K$}]
\end{description}

>>>>

	\item [\parbox{2cm}{$\boldsymbol{H}$}] The event of observing heuristics.
	\item [\parbox{2cm}{$\boldsymbol{E}$}] The event of observing entities.
	\item [\parbox{2cm}{$\boldsymbol{C}$}] The event of observing credit assignments upon meeting credit assignment criteria.
	\item [\parbox{2cm}{$A$}] A random event.
	\item [\parbox{2cm}{$B$}] A random event.
	\item [\parbox{2cm}{$I$}] The maximum number of instances in the replay window.
	\item [\parbox{2cm}{$N$}] The maximum number of random events observed.
	\item [\parbox{2cm}{$J$}] The entity pool (population) size.
	\item [\parbox{2cm}{$K$}] The heuristic pool size.
	\item [\parbox{2cm}{$L$}] The number of credit assignment output classes.
	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}] The concentration parameters for the heuristic probability distribution.
	\item [\parbox{2cm}{$\alpha_{1}$}] The first dimension of the concentration parameter, $\boldsymbol{\alpha}$.
	\item [\parbox{2cm}{$\alpha_{k}$}] The dimension of $\boldsymbol{\alpha}$ associated with class $k$.
	\item [\parbox{2cm}{$\alpha_{K}$}] The $k$-th dimension of the concentration parameter, $\boldsymbol{\alpha}$.
	\item [\parbox{2cm}{$\boldsymbol{\beta}$}] The concentration parameters for the entity-heuristic probability distributions.
	\item [\parbox{2cm}{$\beta_{1}$}] The first dimension of the concentration parameter, $\boldsymbol{\beta}$.
	\item [\parbox{2cm}{$\beta_{2}$}] The second dimension of the concentration parameter, $\boldsymbol{\beta}$.
	\item [\parbox{2cm}{$\beta_{j,k}$}] The $j$-th entity's concentration parameter associated with heuristic $k$.
	\item [\parbox{2cm}{$\boldsymbol{\gamma}$}] The concentration parameters for the credit-heuristic probability distribution.
	\item [\parbox{2cm}{$\gamma_{0}$}] The zeroth dimension of the concentration parameter, $\boldsymbol{\gamma}$.
	\item [\parbox{2cm}{$\gamma_{1}$}] The first dimension of the concentration parameter, $\boldsymbol{\gamma}$.
	\item [\parbox{2cm}{$\gamma_{K}$}] The $k$-th dimension of the concentration parameter, $\boldsymbol{\gamma}$.
	\item [\parbox{2cm}{$\boldsymbol{\theta}$}] The heuristic probability distribution.
	\item [\parbox{2cm}{$\boldsymbol{\phi}$}] The entity-heuristic probability distribution.
	\item [\parbox{2cm}{$\boldsymbol{\psi}$}] The credit-heuristic probability distribution.
	\item [\parbox{2cm}{$Mult$}] The Multinomial probability distribution.
	\item [\parbox{2cm}{$h_{i,k}$}] The realisation of the $i$-th event of observing heuristic $k$.
	\item [\parbox{2cm}{$\theta_{k}$}] The heuristic selection probability for heuristic $k$.
	\item [\parbox{2cm}{$\mathbbm{1}_{0}$}] The indicator function yielding a failure/non-occurrence.
	\item [\parbox{2cm}{$\mathbbm{1}_{1}$}] The indicator function yielding a success/occurrence.
	\item [\parbox{2cm}{$N_{k}$}] A summary variable denoting the count of occurrences of the event $h_{i}$ taking on class $k$ in $I$ independent, identical runs.
	\item [\parbox{2cm}{$e_{i,j,k}$}] The realisation of the $i$-th event of observing heuristic $k$ for selected for entity $j$.
	\item [\parbox{2cm}{$\phi_{j,k}$}] The entity-heuristic selection probability for entity $j$ and heuristic $k$.
	\item [\parbox{2cm}{$N_{j,k}$}] A summary variable denoting the count of occurrences of the events $e_{i}$ taking on class $j$ and $h_{i}$ taking on class $k$ in $I$ independent, identical runs.
	\item [\parbox{2cm}{$k$}] Index generally associated to heuristic $k$.
	\item [\parbox{2cm}{$j$}] Index generally associated to entity $j$.
	\item [\parbox{2cm}{$i$}] Index generally associated to event/run $i$.
	\item [\parbox{2cm}{$h_{i}$}] The $i$-th event of observing heuristics.
	\item [\parbox{2cm}{$c_{i,k}$}] The realisation of the $i$-th event of observing a credit assignment $i$ to heuristic $k$.
	\item [\parbox{2cm}{$\psi_{k}$}] The heuristic-credit-assignment probability for credit assignment success and heuristic $k$.
	\item [\parbox{2cm}{$N_{0,k}$}] The count of occurrences of the events $c_{i}$ taking on a failure.
	\item [\parbox{2cm}{$N_{1,k}$}] The count of occurrences of the events $c_{i}$ taking on a success.
	\item [\parbox{2cm}{$c_{i}$}] The $i$-th event of observing credit assignments.
	\item [\parbox{2cm}{$LSE$}] The log-sum-exp trick/function.
	\item [\parbox{2cm}{$\hat{\theta}_{k}$}] The expected value of the probability of selecting heuristic $k$.
	\item [\parbox{2cm}{$E[\theta_{k}]$}] The expected value of the probability of selecting heuristic $k$.
	\item [\parbox{2cm}{$N_{j}$}] The count of the occurrences of observing entity $j$.
	\item [\parbox{2cm}{$\hat{\phi}_{j,k}$}] The expected value of the probability of selecting heuristic $k$ for entity $j$.
	\item [\parbox{2cm}{$E[\phi_{j,k}]$}] The expected value of the probability of selecting heuristic $k$ for entity $j$.
	\item [\parbox{2cm}{$\hat{\psi}_{k}$}] The expected value of the probability of selecting heuristic $k$ and observing credit assignments.
	\item [\parbox{2cm}{$E[\psi_{k}]$}] The expected value of the probability of selecting heuristic $k$ and observing credit assignments.
	\item [\parbox{2cm}{$\boldsymbol{\hat{\theta}}$}] The expected value of the heuristic selection probabilities.
	\item [\parbox{2cm}{$\boldsymbol{\hat{\phi}}$}] The expected value of the entity-heuristic probabilities.
	\item [\parbox{2cm}{$\boldsymbol{\hat{\psi}}$}] The expected value of the heuristic-credit-assignment probabilities.
	\item [\parbox{2cm}{$\boldsymbol{\lambda}$}] Error vector.
	\item \item [\parbox{2cm}{$\lambda_{1}$}] The first dimension of the error vector, $\boldsymbol{\lambda}$.
	\item [\parbox{2cm}{$\lambda_{j}$}] The $j$-th dimension of the error vector, $\boldsymbol{\lambda}$.
	\item [\parbox{2cm}{$\lambda_{J}$}] The last dimension of the error vector, $\boldsymbol{\lambda}$ in $J$ dimensions.
	\item [\parbox{2cm}{$\epsilon$}] Error factor.
	\item [\parbox{2cm}{$\gamma_{1,k}$}] The first dimension of the concentration parameter, $\boldsymbol{\gamma}$ associated with heuristic $k$.
	\item [\parbox{2cm}{$\gamma_{2,k}$}] The second dimension of the concentration parameter, $\boldsymbol{\gamma}$ associated with heuristic $k$.
	\item [\parbox{2cm}{$\alpha$}] Concentration parameter for the Beta probability distribution.
	\item [\parbox{2cm}{$\beta$}] Concentration parameter for the Beta probability distribution.

	\item [\parbox{2cm}{$\eta$}] Learning rate.
	\item [\parbox{2cm}{$\mathcal{A}(v)$}] Functional form of priors.
	\item [\parbox{2cm}{$\psi_{k}$}] The successful credit assignment probability for heuristic $k$.
	\item [\parbox{2cm}{$c_{1}$}] Successful credit allocation.
	\item [\parbox{2cm}{$e_{i}$}] The $i$-th event of observing entities.
	\item [\parbox{2cm}{$e_{j}$}] The $j$-th entity.
	\item [\parbox{2cm}{$h_{k}$}] The $k$-th heuristic.
	\item [\parbox{2cm}{$S$}] The probability simplex.
	\item [\parbox{2cm}{$t$}] Time step.
\end{description}

@@

\begin{description}
	\item [\parbox{2cm}{$\alpha_{0}$}] The zeroth dimension of the concentration parameter $\boldsymbol{\alpha}$ and is associated to heuristic $0$ (\acs{SGD}).
	\item [\parbox{2cm}{$\alpha_{6}$}] The sixth dimension of the concentration parameter $\boldsymbol{\alpha}$ and is associated to heuristic $6$ (\acs{Adam}).
	\item [\parbox{2cm}{$\alpha_{7}$}] The seventh dimension of the concentration parameter $\boldsymbol{\alpha}$ and is associated to heuristic $7$ (\acs{PSO}).
	\item [\parbox{2cm}{$\alpha_{8}$}] The eight dimension of the concentration parameter $\boldsymbol{\alpha}$ and is associated to heuristic $8$ (\acs{GA}).
	\item [\parbox{2cm}{$\alpha_{i}$}] The $i$-th dimension of the concentration parameter $\boldsymbol{\alpha}$ and is associated to heuristic $i$.
	\item [\parbox{2cm}{$\boldsymbol{H}$}] The event of observing heuristics.
	\item [\parbox{2cm}{$\boldsymbol{E}$}] The event of observing entities.
	\item [\parbox{2cm}{$\boldsymbol{C}$}] The event of observing credit assignments upon meeting credit assignment criteria.
	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}] The concentration parameters for the heuristic probability distribution.
	\item [\parbox{2cm}{$\boldsymbol{\phi}$}] The entity-heuristic probability distribution.
	\item [\parbox{2cm}{$\boldsymbol{\psi}$}] The credit-heuristic probability distribution.
	\item [\parbox{2cm}{$\boldsymbol{\theta}$}] The heuristic probability distribution.
	\item [\parbox{2cm}{$\theta_{0}$}] The zeroth dimension of the heuristic selection probabilities $\boldsymbol{\theta}$ and is associated to heuristic $0$ (\acs{SGD}).
	\item [\parbox{2cm}{$\theta_{6}$}] The sixth dimension of the heuristic selection probabilities $\boldsymbol{\theta}$ and is associated to heuristic $6$ (\acs{Adam}).
	\item [\parbox{2cm}{$\theta_{7}$}] The seventh dimension of the heuristic selection probabilities $\boldsymbol{\theta}$ and is associated to heuristic $7$ (\acs{PSO}).
	\item [\parbox{2cm}{$\theta_{8}$}] The eight dimension of the heuristic selection probabilities $\boldsymbol{\theta}$ and is associated to heuristic $8$ (\acs{GA}).
	\item [\parbox{2cm}{$c_{1}$}] Successful credit allocation.
	\item [\parbox{2cm}{$Cat$}] The Categorical probability distribution.
	\item [\parbox{2cm}{$Dir$}] The Dirichlet probability distribution.
	\item [\parbox{2cm}{$e_{0}$}] Entity $0$.
	\item [\parbox{2cm}{$h_{0}$}] Heuristic $0$ (\acs{SGD}).
	\item [\parbox{2cm}{$h_{6}$}] Heuristic $6$ (\acs{Adam}).
	\item [\parbox{2cm}{$h_{7}$}] Heuristic $7$ (\acs{PSO}).
	\item [\parbox{2cm}{$h_{8}$}] Heuristic $8$ (\acs{GA}).
	\item [\parbox{2cm}{$i$}] General index associated with event/run number.
	\item [\parbox{2cm}{$K$}] Heuristic pool size.
\end{description}
